Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-29 awipev-CO2.Rmd
Updated linksat the end

```{r save all, echo=FALSE, message= FALSE, warning=FALSE}
# d_hour is the real data set that is read at the beginning of the script
# d_all comprises additional columns calculated in this script
d_all$at <- ifelse(is.nan(d_all$at), NA, d_all$at) # replace all NaN by NA
d_all$ct <- ifelse(is.nan(d_all$at), NA, d_all$ct) # replace all NaN by NA
dplyr::mutate(d_all, month = as.factor(month(x = datetime, label = TRUE)))

saveRDS(file= paste0(path, "fb_data/d_all.rds"), d_all)
```

@@

[wiki document](https://spaces.awi.de/confluence/login.action?os_destination=%2Fpages%2Fviewpage.action%3FspaceKey%3DMOS%26title%3DWater%2Bsampling&permissionViolation=true)

@@

@@

>>>>

```{r save all, echo=FALSE, message= FALSE, warning=FALSE}
# d_hour is the real data set that is read at the beginning of the script
# d_all comprises additional columns calculated in this script
d_all$at <- ifelse(is.nan(d_all$at), NA, d_all$at) # replace all NaN by NA
d_all$ct <- ifelse(is.nan(d_all$at), NA, d_all$ct) # replace all NaN by NA
dplyr::mutate(d_all, month = as.factor(month(x = datetime, label = TRUE)))
saveRDS(file= paste0(path, "fb_data/d_all.rds"), d_all)

pangaea <- as_tibble(d_all) %>% 
  dplyr::select(datetime, pressure_insitu_ctd, sal_insitu_ctd, sal_fb, sal_mix, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, temp_dur, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, pco2_corr, pco2_calc_fb, at_calc, ph_dur_corr, pHint_tot_sf) %>%
  dplyr::rename(pressure = pressure_insitu_ctd,
                s_insitu = sal_insitu_ctd,
                s_fb = sal_fb, 
                s_mix = sal_mix,
                t_11m = temp_insitu_11m,
                t_insitu = temp_insitu_ctd, 
                t_fb = temp_fb, 
                t_sf = temp_sf, 
                t_dur = temp_dur, 
                at = at, 
                at_calc =at_calc,
                ct = ct, 
                ph_s_sf_t_insi = ph_s_sf_temp_insi, 
                ph_s_dur_t_fb = ph_s_dur_temp_fb,
                pco2 = pco2_corr,
                pco2_calc = pco2_calc_fb,
                pH_sf = pHint_tot_sf,
                ph_dur = ph_dur_corr
                )
saveRDS(file= paste0(path, "fb_data/pangaea.rds"), pangaea)
write_csv(pangaea, path = paste0(path, "fb_data/pangaea.csv"))
# Metadata Pangaea
# pressure = pressure in situ (profiler)
# s_insitu = salinity in situ (profiler)
# s_fb = salinity in FerryBox 
# s_mix = salinity in FerryBox with gaps filled by s_insitu below 8 m
# t_11m = temperature in situ at 11 m
# t_insitu = temperature in situ (profiler), 
# t_fb = temperature in FerryBox 
# t_sf = temperature SeaFET (profiler), °C
# t_dur = temperature Durafet (FerryBox)
# at = total alkalinity, discrete measurements (FerryBox)
# at_calc = total alkalinity, calculated from salinity
# ct = dissolved inorganic carbon, discrete measurements (FerryBox)
# ph_s_sf_t_insi = pH spectrophotometric SeaFET in situ (11 m)
# ph_s_dur_t_fb = pH spectrophotometric Durafet in FerryBox
# pco2 = pCO2 in Ferrybox
# pco2_calc = pCO2 calculated in the FerryBox calculated from discrete measurments of AT and CT
# pH_sf = pH SeaFET at in situ temperature (profiler)
# ph_dur = pH Durafet at FerryBox temperature (FerryBox)
```

@@

[wiki document](https://spaces.awi.de)

@@

[Logbook FerryBox](https://docs.google.com/spreadsheets/d/1QwAJm7TttoEwue-CUM0efhqEAMwj5m148Gy_Mp-1maM/edit?ts=5ed0fca6#gid=2036495380)

@@

[Dashboard](https://dashboard.awi.de/?dashboard=3760)
